Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-04 paper/ms.tex
Add caption to many orbits

\begin{figure*}
\plotone{fig/many_orbits_schmactions.pdf}
\caption{Caption.}
\label{fig:many_orbit_wrong_ref}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/many_orbits_schmactions.pdf}
\caption{\Gus{update figure} We report the 95\uth minus 5\uth percentile of the error in the
measured action ($\Delta J_i$) from coordinate system errors for three orbits
with low-, medium-, and high-$J_z$ values (blue, orange, and red,
respectively). The {\em left}, {\em center}, and {\em right} panels show the
result for $J_r$, $L_z$, and $J_z$, respectively. The {\em upper} panels
consider an offset in $z$ and the {\em lower} panels consider an offset in $x$
(equivalently, an offset in the Solar radius).}
\label{fig:many_orbit_wrong_ref}
\end{figure*}
